SecFFT: Safeguarding Federated Fine-tuning for Large Vision Language Models against Covert Backdoor Attacks in IoRT Networks

### 2024-11-01 response.tex

% comment14
\rcomment{
\color{red} Several hyperparameters are used in the experiments, but their rationale and appropriateness are not explained. Please provide a justification for their settings.
}
% 1. 为什么使用lora微调，而不用其他微调方式
% 因为受限的计算资源导致对CLIP模型进行全量微调的时间成本非常之大，同时，我们的研究重点也不强调微调后的模型具有极高的性能，因此我们放弃了全量微调。目前也存在一些针对CLIP模型的微调方式，比如prompt engineering层面的CoOp、CoCoOp、MaPLe以及adapter层面的CLIP Adapter、TIP-Adapter，但这几个工作微调涉及到的参数量较小，与我们工作假设的高维场景不太契合。综上，我们选择了使用lora方式对CLIP模型进行微调，在微调成本和涉及到的参数量之间能够达到平衡。
% 2. 为啥只对visual-encoder部分进行lora微调
% 我们的工作专注于联邦学习过程中的抗后门攻击，因此在CLIP模型微调这方面，我们采用了最基础的设置。参考CLIP-Adapter这篇文章，因为本文设定的场景是增加视觉大模型在zero-shot下对图像的识别能力，因此我们只对CLIP模型的visual-encoder部分进行lora微调，而对于text-encoder这部分，我们采用“a photo of a {CLASS}"作为文本方面的提示词模板。
% 3. 使用lora对CLIP模型进行微调，相应超参数设置的理由
% 在使用lora对CLIP模型进行微调时，我们所使用的超参数设置参考了CLIP-LORA这篇文章，相关的超参数例如learning rate, batch size等与该篇论文几乎相符合。而在lora参数秩的设置上，如果按照CLIP-LORA这篇文章进行设置则会导致最终微调涉及到的参数量较少，不符合本文设定的场景，因此我们进行了适当增大。
% 4. 联邦训练过程相应的超参数设置理由
% 对于联邦学习相关的超参数例如节点数量，我们的设置参考了\cite{wei2023personalized}, \cite{ilhan2023scalefl}, \cite{wu2023faster}, \cite{ye2024openfedllm}, \cite{zhou2024every}, \cite{nguyen2022flame}, and \cite{yang2024roseagg}等文章。这些工作所采用的节点数不尽相同，范围从20到200不等。因此，综合考虑时间成本，计算开销以及验证效果等方面，我们才采用相应的超参数设置。
% Thank you for your valuable feedback. We appreciate your comments regarding the need for clarification and justification of the hyperparameter settings used in our experiments. Below, we provide a detailed response to address your concerns:

% \textbf{Rationale behind hyperparameter settings for LoRA fine-tuning of CLIP:}
% We chose LoRA (Low-Rank Adaptation) for fine-tuning the CLIP model due to limited computational resources and the need to balance time cost and parameter efficiency. Full fine-tuning of the CLIP model is computationally expensive, and since our research does not prioritize pushing the fine-tuned model to peak performance, we selected LoRA to maintain computational efficiency while still allowing a sufficient degree of fine-tuning. LoRA enables us to adjust a smaller set of parameters, which is more practical for the high-dimensional data scenarios we explore in our work.
% For the specific hyperparameters used in LoRA fine-tuning, we referred to the values suggested in the CLIP-LORA paper, such as learning rate and batch size. However, we found that the original rank setting of LoRA would have resulted in an insufficient number of parameters for our scenario. Thus, we adjusted the rank to increase the number of tunable parameters, ensuring that the model's capacity aligns with the complexity of the data used in our experiments.

% Rationale behind the hyperparameter settings for federated training
% For the federated training process, we carefully considered the hyperparameters, especially the number of participating nodes, which is a critical factor in federated learning. Informed by recent studies such as \cite{wei2023personalized}, \cite{ilhan2023scalefl}, and \cite{wu2023faster}, which tested node counts ranging from 20 to 200, we aimed to find a balance between computational cost, time efficiency, and model accuracy. After evaluating our available resources and validating our preliminary results, we settled on a configuration that fits the scope of our work while ensuring robust performance.

Thank you for your insightful comments. We have carefully considered your concerns regarding the hyperparameter settings and provide a detailed explanation below:

\textbf{LoRA was selected due to computational efficiency and alignment with our research goals:}
Given the limited computational resources available, full-parameter fine-tuning of the CLIP model was impractical due to the substantial time and resource costs. Additionally, our research does not focus on achieving the highest possible performance but rather on efficiently conducting experiments. While other fine-tuning methods like CoOp\cite{zhou2022learning}, CoCoOp\cite{zhou2022conditional}, MaPLe, and adapter-based methods such as CLIP-Adapter\cite{gao2024clip} and TIP-Adapter\cite{zhang2021tip} are available, these involve fewer parameters and do not align well with the high-dimensional scenarios required in our study. LoRA offers a balanced solution, maintaining computational efficiency while optimizing parameter adjustment.

\textbf{The visual encoder of the CLIP model was fine-tuned to meet the core focus of our research:}
Our study primarily addresses backdoor attacks in federated learning, and thus we used a straightforward configuration for fine-tuning the CLIP model. In accordance with the approach from the CLIP-Adapter\cite{gao2024clip} paper, which enhances visual recognition capabilities, we applied LoRA exclusively to the visual encoder. For the text encoder, we retained the default prompt template (“a photo of a \{CLASS\}”) to guide text-based predictions, which met our research needs without introducing unnecessary complexity.

\textbf{The hyperparameters for LoRA were adapted based on the demands of our experimental setup:}
We adopted hyperparameters such as learning rate and batch size from the recommendations in the CLIP-LORA\cite{zanella2024low} paper. However, we determined that the default rank for LoRA parameters was insufficient to meet the high-dimensional requirements of our work. To better accommodate the parameter complexity in our experiments, we adjusted the rank to increase the number of tunable parameters, ensuring better fitting the requirements of our high-dimensional scenario.

\textbf{Federated learning hyperparameters were informed by prior studies and practical considerations:}
For the federated training aspect of our research, we relied on previous studies, including \cite{wei2023personalized}, \cite{ilhan2023scalefl}, and \cite{wu2023faster}, which suggested a participants range from 20 to 200. Considering the time cost, computational overhead, and  the effectiveness of experimental results, we selected the most suitable configuration for our experiments, optimizing both performance and resource use.

% comment15
\rcomment{
\color{red} Why is the condition $\zeta T$ set in the optimization problem in Section V.2? Clarification is needed.
}
